Robust Bayesian Analysis of Causal Inference Problems

### 2024-03-22 JASA-template.tex
Small fixes.

We present our analyses in \cref{tab:causal} and \cref{tab:misspec}.
For the sake of clarity we use the following accronyms: RBCE for 
robust Bayesian causal estimation (our method); SSCE for spike and
slab causal estimation \cite{koch2020}; BSSCE for bi-level spike and slab causal
estimation \cite{koch2020}; and BSSL for Bayesian spike and slab lasso
\cite{xu2015}. As it can be
seen from both the tables, SSCE and BSSCE are formulated for problems
where $p\le n$ and therefore we do not have any results for $n<50$.

>>>>

We present our analyses in \cref{tab:causal,tab:misspec}.
For the sake of clarity we use the following accronyms: RBCE for 
robust Bayesian causal estimation (our method); SSCE for spike and
slab causal estimation \cite{koch2020}; BSSCE for bi-level spike and slab causal
estimation \cite{koch2020}; and BSSL for Bayesian spike and slab LASSO
\cite{xu2015}. As it can be
seen from both the tables, SSCE and BSSCE are formulated for problems
where $p\le n$ and therefore we do not have any results for $n<50$.
